### 2020-04-26 ThesisJo/3_publications.tex
2020-04-26

%
%\paper{I} describes the use and implementation of the \gls{MVDR} beamformer in active sonar imaging in its most general and exact form. 
%
%Its widespread use and generic implementation makes it the reference. thus will be considered the reference method. , and this will be referred to as a fully adaptive technique. Due to its ability to analytically  to apply the minimum variance criteria in an exact manner, Due to its popularity and We view this as the reference method for We refer to it as fully adaptive since it computes analytically evaluates   yields  This is a fully adaptive method   This method is  on a \gls{GPGPU} for active sonar imaging. This is to prove that using a \gls{MVDR}
%
%Paper II takes the \gls{MVDR} method and applies it to clinical Ultrasound Imaging
%
%
%We point out important hardware limitations for these devices, and assess the design in terms of how efficiently it is able to use the GPU's resources. On a quad-core Intel Xeon system with a high-end Nvidia GPU, our GPU implementation renders more than a million pixels per second (1\;MP/s). Compared to our initial central processing unit (CPU) implementation the optimizations described herein led to a speedup of more than two orders of magnitude, or an expected five to ten times improvement had the CPU received similar optimization effort. This throu

% Classification accuracy
% Logarithmic loss
% Confusion matrix
% Area under curve
% F1 score
% Mean absolute error
% Mean squared error
%
%

We present four journal published papers concerned with \emph{adaptive} and \emph{hardware accelerated} formation of acoustic images: the first three through \emph{reconstruct} from echoes and the last \emph{synthesizes} through simulation.

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\section{Paper I}\label{sec:paperI} %
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\textbf{An Optimized GPU implementation of the\\MVDR Beamformer for Active Sonar Imaging}~\cite{Buskenes2014}\\
J.I. Buskenes, J.P. Åsen, C.-I.C. Nilsen and A. Austeng\\
\textit{IEEE Journal of Oceanic Engineering}\\
Volume 40, Issue 2, April 2015

>>>>

%
%\paper{I} describes the use and implementation of the \gls{MVDR} beamformer in active sonar imaging in its most general and exact form. 
%
%Its widespread use and generic implementation makes it the reference. thus will be considered the reference method. , and this will be referred to as a fully adaptive technique. Due to its ability to analytically  to apply the minimum variance criteria in an exact manner, Due to its popularity and We view this as the reference method for We refer to it as fully adaptive since it computes analytically evaluates   yields  This is a fully adaptive method   This method is  on a \gls{GPGPU} for active sonar imaging. This is to prove that using a \gls{MVDR}
%
%Paper II takes the \gls{MVDR} method and applies it to clinical Ultrasound Imaging
%
%We point out important hardware limitations for these devices, and assess the design in terms of how efficiently it is able to use the GPU's resources. On a quad-core Intel Xeon system with a high-end Nvidia GPU, our GPU implementation renders more than a million pixels per second (1\;MP/s). Compared to our initial central processing unit (CPU) implementation the optimizations described herein led to a speedup of more than two orders of magnitude, or an expected five to ten times improvement had the CPU received similar optimization effort. This throu

% Classification accuracy
% Logarithmic loss
% Confusion matrix
% Area under curve
% F1 score
% Mean absolute error
% Mean squared error
%
%Some text Some other text Some other text Some other text Some other text Some other text Some other text Some other text Some other text Somet
%
%Some text Some other text Some other text Some other text Some other text Some other text Some other text Some other text Some other text Someth

%\quotesave{somequote}{
%Some text Some other text Some other text Some other text Some other}

We present four journal published papers concerned with \emph{adaptive} and \emph{hardware accelerated} formation of acoustic images: the first three \emph{reconstruct} images from echoes and the last \emph{synthesizes} through simulation.

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\section{Paper I}\label{sec:paperI} %
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\textbf{An Optimized GPU implementation of the\\MVDR Beamformer for Active Sonar Imaging}~\cite{Buskenes2014}\\
J.I. Buskenes, J.P. Åsen, C.-I.C. Nilsen and A. Austeng\\
\textit{IEEE Jou\textbf{}rnal of Oceanic Engineering}\\
Volume 40, Issue 2, April 2015
